%*******************************************************
% Abstract in English
%*******************************************************
\pdfbookmark[0]{Abstract}{Abstract}


\begin{otherlanguage}{american}
	\chapter*{Abstract}
	Today’s blockchain ecosystem has spread into multiple chains using different consensus algorithms and architectures. After a decade of blockchain applications and development there is a need for interoperability between upcoming and current blockchain innovations. Interoperability presents a complex task due to the architectural differences of blockchain technologies, to swap assets and tokens between chains in a steadily growing environment. This ecosystem consists of many chains without any interoperability. For example if Alice wants to trade her bitcoin with Bob's ether they have to use a centralized exchange, which exposes them to the possibility of scam, fraud and malicious hacks. This thesis provides a prototype with a three-way swap between three ethereum blockchains, to execute such a swap between bitcoin and ethereum further research is needed since bitcoin's script language is not suited for swaps at this time. Atomic Cross-Chain Swaps propose a small step towards interoperability of blockchains, by removing the intermediate parties such as exchanges. Blockchain interoperability enables more security for the end-user and closes attack vectors for fraudulent actors.
	
	% In bitcoin with Bob's ether
	% Does this thesis allow bitcoin <-> Ether swaps? If not, either don't promise it, or (better) add a sentence explaining what is (and what is not) in this thesis -- i.e. a prototype that shows... (what exactly?).
	%This thesis provides a prototype with a three-way swap between three ethereum blockchains posing as bitcoin chain, car-title chain and alt-coin chain. 
	%This thesis provides a prototype with a three-way swap between three ethereum blockchains, to execute such a swap between bitcoin and ethereum further research is needed since bitcoin's script language is not suited for swaps at this time.
	
	
	
	%Short summary of the contents in English. Approximately one page\dots
	%\medskip
	
	%\noindent
	%BTW: A great guide by Kent Beck how to write good abstracts can be found here:
	%\begin{center}
		%\url{https://plg.uwaterloo.ca/~migod/research/beckOOPSLA.html}
	%\end{center}
\end{otherlanguage}
